The language of generalization: Probability, vagueness, and interaction

### 2018-02-06 paper/case1-generics.Rmd
move code from case1 to analysis file, cache results

### Method
```{r eval = F}
d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments-n100.csv", sep = ""))
d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "naturalGenerics-trials-formatted.csv", sep = ""))

# write.csv(
#   left_join(
#   d1 %>%
#     mutate(sentence = as.character(sentence),
#            sentence = gsub('&quotechar', '', sentence),
#          sentence = gsub('lyme', 'Lyme', sentence)),
#   unique(d2 %>%
#     mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
#     select(Category, Property, sentence))
# ), file = paste(project.path, "data/generics/endorsement/",
#                     "truth-judgments-n100.csv", sep = ""), row.names = F)
```

```{r generic-endorsement}
d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments_catch-trials.csv", sep = ""))

d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments-n100.csv", sep = ""))

d.gen.endorse.summary <- left_join(
  d.gen.endorse, 
  d.gen.endorse.catch %>% select(workerid, pass)
  ) %>%
  filter(pass == 1) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0)) %>%
  group_by(sentence) %>%
  multi_boot_standard(col = "response") %>%
  ungroup() %>%
  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))

d.gen.endorse.bayes <- left_join(
  d.gen.endorse, 
  d.gen.endorse.catch %>% select(workerid, pass)
  ) %>%
  filter(pass == 1) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence)) %>%
  group_by(sentence) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b)) %>% 
  ungroup()

d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
                       "naturalGenerics-prior-trials-n57.csv", sep = ""))

d.prev.summary <- d.prev %>%
  mutate(item = paste(Category, " ", Property, ".", sep = "")) %>%
  filter(item %in% d.gen.endorse.bayes$sentence) %>%
  mutate(prevalence = prevalence / 100) %>%
  group_by(Category, Property, item) %>%
  multi_boot_standard(col = "prevalence")

# d.gen.endorse.summary %>%
#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
generics.endorsement.spectrum <- left_join(
  d.gen.endorse.bayes, d.prev.summary %>% rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper)
) %>%
  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))  %>%
  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev))+
  geom_bar(stat = 'identity', position = position_dodge(), color= 'black', alpha = 0.9)+
  geom_linerange(position = position_dodge())+
  #geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Human generic endorsement")+
  xlab("")+
  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
  scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
  guides(fill = guide_colorbar(title = 'Prevalence',
                               ticks = F))+
  theme(legend.position = 'bottom')
  #geom_hline(yintercept = -0.25, lty = 3)+
  #geom_hline(yintercept = 0.25, lty = 3)
```

@@

mht.truth.judgments <- data.frame(sentence = names(all.sentences),
           truth_judgment = as.vector(unlist(all.sentences)))

d.gen.endorse.manipulation.check.bayes <- left_join(
  left_join(
    d.gen.endorse, 
    d.gen.endorse.catch %>% select(workerid, pass)
    ),
  mht.truth.judgments ) %>%
  filter(pass == 1) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence)) %>%
  group_by(truth_judgment) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b)) %>% 
  ungroup() %>%
  mutate(truth_judgment = factor(truth_judgment, levels = truth_judgment[order(MAP_h)]))

@@

uncertain_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"MAP_h"]]
uncertain_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"low"]]
uncertain_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"high"]]

```

@@

```{r generic-endorsement-priors}
# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time

d.gen.endorse.priors <- read.csv(paste(project.path, 
                                       "data/generics/endorsement/",
                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
gen.endorse.properties <- levels(d.gen.endorse.priors$Property)

genericEndorsementPriorModelHelpers <- '
var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var avoidEndPoints = function(x){
  x == 0 ? eps : 
  x == 1 ? 1 - eps : 
  x
}

var betaShape = function(params){
  return {
      a: params.g * params.d,
      b : (1-params.g) * params.d
  }
}

var preprocessedResponses = map(function(d){
  return avoidEndPoints(d / 100)
}, data)
'

structuredPriorModel <- '
var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })
  return {g, d, phi}
}
'

unstructuredPriorModel <- '
var model = function(){
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  mapData({data: preprocessedResponses}, function(d){
    factor(stableComponent.score(d))
  })
  return {g, d}
}
'
genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")

```

```{r generic-endorsement-priors-unbounded, eval = F}
# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time

d.gen.endorse.priors <- read.csv(paste(project.path, 
                                       "data/generics/endorsement/",
                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
gen.endorse.properties <- levels(d.gen.endorse.priors$Property)

unboundedModel <- '
var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var avoidEndPoints = function(x){
  x == 0 ? eps : 
  x == 1 ? 1 - eps : 
  x
}

var preprocessedResponses = map(function(d){
  return avoidEndPoints(d / 100)
}, data)

var shapeParams = function(params){
  return {
    a: params.g * params.d,
    b: (1 - params.g) * params.d
  }
}

var model = function(){

  // var numComponents = (1 + poisson(1));
  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
    return uniformDrift({a: 0, b:1, width: 0.2})
  }))).reverse()

  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
  var componentParams = map(function(i){
    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
    var betaParams = shapeParams({g, d})
    return betaParams
  }, _.range(numComponents))

  mapData({data: preprocessedResponses}, function(d){

    var scr = log(sum(map(function(cParams){
      cParams[1] * exp(Beta(cParams[0]).score(d))
    }, _.zip(componentParams, mixtureWeights))))
//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
    factor(scr)
  })

  var componentPredictives = map(function(cParams){
      return beta(cParams)
  }, componentParams)

  return _.fromPairs(
    _.zip(
        map(function(i){ i + "_weight" }, _.range(5)), 
        mixtureWeights
      ).concat(
      _.zip(
        map(function(i){ i + "_predictive" }, _.range(5)), 
        componentPredictives
      )
    )
  )//sort(T.toScalars(mixtureWeights))
};
'

example.generics.prior.properties <- c(
  "dont eat people", "have beautiful feathers",
  "have wings", "are red",
  "carry malaria", "lay eggs", 
  "are female", "have spots"
  )
priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
  n_samples <- 10000
lg = 0
  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 1,
                                 cores = 1,
                                 inference_opts =
                                   list(method = "MCMC",
                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))
```

```{r eval = F}
m.gen.endorse.priors.unbounded %>%
      separate(Parameter, into = c("c", "var")) %>% 
      ggplot(., aes( x=  value, fill = c))+
 geom_histogram(position = position_dodge(), binwidth = 0.05)+
 facet_wrap(~var)+
  scale_fill_solarized()
```

```{r generic-endorsement-priors-bayesFactors, eval = F}
genericEndorsementPriorModelPriorLikelihoodHelpers <- '
var properties = _.uniqBy(_.map(data, "Property"));

var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var avoidEndPoints = function(x){
  x == 0 ? eps : 
  x == 1 ? 1 - eps : 
  x
}

var betaShape = function(params){
  return {
      a: params.g * params.d,
      b : (1-params.g) * params.d
  }
}
'

genericEndorsementPriorModelsPriorLikelihood <- '
var transientComponent = Beta({a:1, b:100})

var model = function(){

  var propertyLogLikes = map(function(property){

    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
    var preprocessedResponses = map(function(d){
        return avoidEndPoints(d / 100)
    }, propertyData);

    var phi = uniformDrift({a:0, b: 1, width:0.2});
    var g = uniformDrift({a:0, b: 1, width:0.2});
    var d = uniformDrift({a:0, b: 100, width:5});
    var stableParams = betaShape({g, d})
    var stableComponent = Beta(stableParams)

    var logLikes = map(function(d){
      var structuredLL = log(
        phi * exp(stableComponent.score(d)) +
        (1 - phi) * exp(transientComponent.score(d))
      )

      var unstructuredLL = stableComponent.score(d);

      return {structuredLL, unstructuredLL}
    }, preprocessedResponses)

    return {
      structuredLL: sum(_.map(logLikes, "structuredLL")), 
      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
    }

  }, properties)

  return {
    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
  }
}
'

```

```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
marginal.prior.likelihoods <- data.frame()

# 100 samples takes 30s
m.gen.endorse.priors.logLike <- webppl(
    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
          genericEndorsementPriorModelsPriorLikelihood,
          sep = '\n'), 
    data = d.gen.endorse.priors, data_var = "data",
    model_var = "model", 
    inference_opts = list(method = "forward", samples = 1000),
    chains = 3, cores = 3
) %>% 
  mutate(value = as.numeric(value))

min.ll.1 <- min(
  m.gen.endorse.priors.logLike$value[
    is.finite(
      m.gen.endorse.priors.logLike$value
      )
    ]
  )

m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
  rowwise() %>%
  mutate(value = ifelse(value == -Inf, min.ll.1, value))

save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
```

```{r generic-endorsement-priors-bayesFactorsLoad}
load(file = '../analysis/generics-priors-loglike.Rdata')
marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
  group_by(Chain, Parameter) %>%
  summarize(mll  = logmeanexp(value))

marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
  spread(Parameter, mll) %>%
  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))

roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
```

@@

<!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data. -->
<!-- Indeed, the data strongly suggests the prevalence prior is structured. -->

```{r generic-endorsement-priors-savageDickeyModel, eval = F}
savageDickeyModel <-'
var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })
  return {phi}
}

//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
// var samples = 2000, burn = burn / 2, lag = 0;
var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
verbose: true}, model)
var modelPrior = Infer({method: "forward", samples:10000}, model)

var pointNull = 1;

var logBFs = map(function(diff){
  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
  return [diff, Math.log(savageDickeyRatio)]
}, [0.01, 0.02, 0.03, 0.04, 0.05])

var returnVals = {
  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
}
returnVals
'
```

```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
genericEndorsementPriorSupermodel <- '
var model = function(){
  var alpha = uniformDrift({a:0, b: 1, width:0.2});
  //var structured = flip();
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g1 = uniformDrift({a:0, b: 1, width:0.2});
  var d1 = uniformDrift({a:0, b: 100, width:5});
  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
  // var d0 = uniformDrift({a:0, b: 100, width:5});
  var stableParams1 = betaShape({g: g1, d: d1})//, 
      //stableParams0 = betaShape({g: g0, d: d0});
  var stableComponent1 = Beta(stableParams1)//,
      //stableComponent0 = Beta(stableParams0);

  var transientComponent = Beta({a:1, b:100})
  mapData({data:preprocessedResponses},
    function(d){
    var scr1 = log(phi * exp(stableComponent1.score(d)) +
                    (1 - phi) * exp(transientComponent.score(d)))
    var scr0 = stableComponent1.score(d);
    // display(exp(scr1) + " " + exp(scr0));
    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
    // factor(structured ? scr1 : scr0)
    factor(combined_ll)
  })
  return alpha
}
'
```

```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
for (p in gen.endorse.properties){
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

  m.gen.endorse.priors.supermodel.posterior <- webppl(
    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
    data = priorData, data_var = "data",
    model_var = "model",  chains = 2,
                                 cores = 2,
                                 inference_opts = 
                                   list(method = "MCMC",
                                        samples = 2000, 
                                        burn = 2000, 
                                        lag = 2, 
                                        verbose = T)
    )

  qplot(m.gen.endorse.priors.supermodel.posterior$value)
}
```

```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
var eps = 0.00000001;

var model = function(){
  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
  var d = uniformDraw(_.range(eps, 100, 2))
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  var logLike = sum(map(function(d){
    var scr = log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    )
    return scr
  }, preprocessedResponses))
  return logLike
}
'
genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
var eps = 0.00000001;

var model = function(){
  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
  var d = uniformDraw(_.range(eps, 100, 2))
  var stableParams = betaShape({g, d});
  var stableComponent = Beta(stableParams);
  var logLike = sum(map(function(d){
    return stableComponent.score(d)
  }, preprocessedResponses))
  return logLike
}
'
```

```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
marginal.prior.likelihoods <- data.frame()

for (p in gen.endorse.properties){
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

  m.gen.endorse.priors.logLike.enum1 <- webppl(
    paste(genericEndorsementPriorModelHelpers,
          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
    data = priorData, data_var = "data",
    model_var = "model", 
    inference_opts = list(method = "enumerate")
    )

  m.gen.endorse.priors.logLike.enum0 <- webppl(
    paste(genericEndorsementPriorModelHelpers,
          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
    data = priorData, data_var = "data",
    model_var = "model", 
    inference_opts = list(method = "enumerate")
    )

  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)

  marginal.prior.likelihoods <- bind_rows(
    marginal.prior.likelihoods, 
    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
  )
}

marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))

```

```{r generic-endorsement-priors-model-run, eval = F}
m.gen.endorse.priors.posteriorPredictive <- data.frame()
n_samples <- 1000
lg = 0
example.generics.prior.properties <- c(
  "dont eat people", "have beautiful feathers",
  "have wings", "are red",
  "carry malaria", "lay eggs", 
  "are female", "have spots"
  )

for (p in example.generics.prior.properties ) {
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

    m.gen.endorse.priors.structured <- webppl(
      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 2,
                                 cores = 2,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
      group_by(Iteration, Chain) %>%
      spread(Parameter, value) %>%
      rowwise() %>%
      mutate(
        a = g*d,
        b = (1-g)*d,
        isPresent = rbinom(1, 1, prob = phi),
        prevalence = ifelse(isPresent == 1, 
                           rbeta(n = 1, 
                                 shape1 = a,
                                 shape2 = b),
                           rbeta(n = 1,
                                 shape1 = 1,
                                 shape2 = 100)),
        Property = p, src = "Structured"
      ) %>% ungroup()

    m.gen.endorse.priors.unstructured <- webppl(
      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 2,
                                 cores = 2,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
      group_by(Iteration, Chain) %>%
      spread(Parameter, value) %>%
      rowwise() %>%
      mutate(
        a = g*d,
        b = (1-g)*d,
        prevalence = rbeta(n = 1, 
                                 shape1 = a,
                                 shape2 = b),
        Property = p, src = "Unstructured"
      ) %>% ungroup()

    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
      m.gen.endorse.priors.posteriorPredictive,
      bind_rows(
       m.gen.endorse.priors.structured.predictive %>%
          select( src, Property, prevalence),
      m.gen.endorse.priors.unstructured.predictive %>%
          select( src, Property, prevalence),
      data.frame(Property = p,
                 src = "Data",
                 prevalence = priorData/100)
      )
    )

}
save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')

```

```{r generic-endorsement-priors-figure2, eval = F}
ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("MAP estimate and 95% HDI of Mixture parameter")
```

@@

```{r generic-regression-models}
d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))

d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims_wrongDeployment.json", sep = "")) %>%
  mutate(sentence = paste(category, property))

### Preprocessing
# - Force all responses to lower case. 
# - Remove spaces.
# - Fix mosquito mispellings.
# - Count "deertick" as "tick".
# - Remove plural "s".
# 
# Mark if the produced animal matches the generic of interest.

mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")

d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
  mutate(
    property = gsub("'", "", property),
    Property = gsub("'", "", Property),
    sentence = paste(Category, Property),
    item = paste(category, property))

d.cv.bootstrapped <- data.frame()
resample_n <- length(levels(factor(d.cv$workerid)))
for (i in 1:10){

  d.cv.bsample <- d.cv %>% 
    select(workerid, property, response) %>% 
    spread(property, response) %>% 
    sample_n(resample_n, replace = TRUE) %>%
    gather(property, category, -workerid) %>% 
        group_by(property) %>%
    mutate(n = n(),
           item = paste(category, property)) %>%
    filter(item %in% d.target.items$item) %>%
    group_by(category, property) %>%
    summarize(mentions = n(),
              trials = mean(n), # mean(n) == n, because it's just the number of subjects
              prop = mentions / trials,
              prop = ifelse(is.na(prop), 0.01, prop),
              iteration = i)

  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
}

empiricalLower = function(dist){
  xi <- quantile(dist, 0.025)
  return (xi[["2.5%"]])
}
empiricalUpper = function(dist){
  xi <- quantile(dist, 0.975)
  return (xi[["97.5%"]])
}
empiricalMean = function(dist){
  xi <- quantile(dist, 0.5)
  return (xi[["50%"]])
}

d.gen.cv.summary <- left_join(
    d.target.items %>% select(-sentence),
    d.cv.bootstrapped %>%
      group_by(property) %>%
      summarize(cv_mean = empiricalMean(prop),
                cv_ci_lower = empiricalLower(prop),
                cv_ci_upper = empiricalUpper(prop))
) %>%
  mutate(
    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
  )

# quantile(filter(d.cv.bootstrapped, property == "is red")$prop, c(0.025, 0.5, 0.975))
# 
# d.cv.bootstrapped %>%
#   group_b

# need to filter by items specified with endorsement
# d.gen.cv.summary <- left_join(
#   d.target.items %>% select(-sentence),
#   d.cv %>%
#     rename(category = response) %>%
#     group_by(property) %>%
#     mutate(n = n(),
#            item = paste(category, property)) %>%
#     filter(item %in% d.target.items$item) %>%
#     group_by(category, property) %>%
#     summarize(mentions = n(),
#               trials = mean(n), # mean(n) == n, because it's just the number of subjects
#               prop = mentions / trials)
#   ) %>%
#   mutate(prop = ifelse(is.na(prop), 0.01, prop))

d.gen.endorse.prev.cue <- left_join(
  left_join(
    left_join(
      d.gen.endorse, 
      d.gen.endorse.catch %>% select(workerid, pass)
      ) %>%
      filter(pass == 1) %>%
    rowwise() %>%
    mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence),
          sentence = gsub('[.]', '', sentence)
    ),
    d.prev.summary %>% 
      rename(prev_mean = mean,
             sentence = item,
             prev_ci_lower = ci_lower,
             prev_ci_upper = ci_upper) %>%
      ungroup() %>%
      mutate(sentence = gsub('[.]', '', sentence))
    ),
  d.gen.cv.summary %>% select(-item))

glm.gen.endorse.prev <- glm(response ~ prev_mean, 
              data = d.gen.endorse.prev.cue, family = 'binomial')

glm.gen.endorse.prev.cv <- glm(response ~ prev_mean + cv_mean, 
              data = d.gen.endorse.prev.cue, family = 'binomial')

d.gen.endorse.prev.cue.uniq <- unique(select(
    d.gen.endorse.prev.cue, Property, Category, sentence, 
    prev_mean, prev_ci_lower, prev_ci_upper, cv_mean, cv_ci_lower, cv_ci_upper
  ))

d.gen.endorse.prev.cue.uniq.lower <- d.gen.endorse.prev.cue.uniq %>% 
  select(-prev_mean, -cv_mean) %>% 
  rename(prev_mean = prev_ci_lower,
         cv_mean = cv_ci_lower)
d.gen.endorse.prev.cue.uniq.upper <- d.gen.endorse.prev.cue.uniq %>% 
  select(-prev_mean, -cv_mean) %>% 
  rename(prev_mean = prev_ci_upper,
         cv_mean = cv_ci_upper)

d.gen.endorse.regression.prevalence <- left_join(
  d.gen.endorse.bayes,
  d.gen.endorse.prev.cue.uniq %>%
    mutate(
      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
    ) %>%
    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
) %>% mutate(
  sqErr = (MAP_h - prediction_mean) ^ 2
)

d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
  d.gen.endorse.bayes,
  d.gen.endorse.prev.cue.uniq %>%
    mutate(
      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
      sentence = paste(Category, " ", Property, ".", sep = "")
      )
) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)

d.gen.endorse.regression <- bind_rows(
  d.gen.endorse.regression.prevalence.cuevalidity %>%
    mutate(src = "regression_Prev_Cuevalidity"),
  d.gen.endorse.regression.prevalence %>% 
    mutate(src = "regression_Prev")
  )

r2.gen.n <- length(d.gen.endorse.bayes$sentence)
r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
mse.gen.regression.prev <-  round(mean(d.gen.endorse.regression.prevalence$sqErr), 3)

@@

```{r generic-RSAmodels, fig.width = 8}
example.generics <- c("Tigers dont eat people", 
                      "Mosquitos carry malaria", 
                      "Robins lay eggs", 
                      "Robins are female",
                      "Leopards have spots")

n_chains <- 3
n_samples <- 100000
burn <- n_samples / 2
lg <- 20

model_prefix <- "results-generics-jointModel-S1-smntcs_"
#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-"
# m.samp <- data.frame()
#m.samp.fixed <- data.frame()
#for (i in seq(1, n_chains)){
  #mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
  #                  n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  #m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))

>>>>

```{r generic-endorsement}
load("cached_results/case1_endorseSummary_byItem.RData") # d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes
generics.endorsement.spectrum <- ggplot(
    d.gen.endorse.bayes.prev, 
    aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
  )+
  geom_bar(stat = 'identity', position = position_dodge(), color='black',  alpha = 1)+
  geom_linerange(position = position_dodge(), size = 1)+
  coord_flip()+
  ylab("Human generic endorsement")+
  xlab("")+
  scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1))+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
  guides(color = guide_colorbar(title = 'Prevalence',
                               ticks = F))+
  theme(legend.position = 'bottom')
```

@@

@@

uncertain_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"MAP_h"]]
uncertain_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"low"]]
uncertain_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"high"]]
```

@@

@@

@@

```{r}
load("cached_results/case1_regressionResults.RData") # d.gen.endorse.regression.prevalence, d.gen.endorse.regression.prevalence.cuevalidity, d.gen.endorse.regression,
r2.gen.n <- length(d.gen.endorse.bayes.prev$sentence)
r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
mse.gen.regression.prev <-  round(mean(d.gen.endorse.regression.prevalence$sqErr), 3)

@@

```{r generic-model-scatters, cache = F}
load("cached_results/case1_modelPosteriors.RData")
#d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt

r2.gen.rsa.generics <- compute_r2(
  d.gen.endorse.rsa.regression %>% filter(src == "Uncertain semantics model"), 
  "prediction_mean", "MAP_h", sigfigs = 4
)

r2.gen.rsa.fixed <- compute_r2(
  d.gen.endorse.rsa.regression %>% filter(src == "Fixed semantics model"),  
  "prediction_mean", "MAP_h", sigfigs = 4
)

mse.gen.rsa.generics <- compute_mse(
  d.gen.endorse.rsa.regression %>% filter(src == "Uncertain semantics model"), 
  "prediction_mean", "MAP_h", sigfigs = 5
)
